---
title: "Appendix"
subtitle: "Educational Mobility and Attitudes Towards Social Justice in Europe"
author: 
    - Daniel Capistrano
    - Mathew Creighton
    - Ebru Işıklı
format: html
  # pdf:
  #   link-citations: true
  #   include-in-header: 
  #     text: |
  #       \usepackage{typearea}
toc: false
number-sections: true
execute:
    echo: false
    warning: false
    message: false
    cache: false
---

```{r}
library(gt)
```

# Introduction

In this appendix, we include additional tables and tests from the paper `TITLE`.

\newpage

<!-- changing the orientation to landscape --------------------------------- -->

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

# Pooled sample

```{r}
#| label: tbl-afull
#| tbl-cap: "Full model estimates for the pooled sample"

# Running code to generate the raw Table1
source("./code/2_Estimates.R")

# Generating formatted table

tab_output |>
  mutate(label = ifelse(label == "(Intercept)", "Intercept", label) ) |>
  mutate(variable = case_match(variable, 
                "eisced" ~ "Educ. attain. (Resp.)",
                "eiscedp" ~ "Educ. attain. (Parent.)",
                #"age_group" ~ "Age group",
                "gender" ~ "Gender",
                "income_feeling" ~ "Feeling about income",
                "(Intercept)" ~ "Intercept",
                .default = variable)) |>
  gt(groupname_col = "variable", rowname_col = "label") |>
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Equality", columns = starts_with("equality")) |>
  tab_spanner(label = "Equity", columns = starts_with("equity")) |>
  tab_spanner(label = "Need", columns = starts_with("need")) |>
  tab_spanner(label = "Entitlement", columns = starts_with("entitlement")) |>
  cols_label(ends_with("_estimate") ~ "Estimate",
            ends_with("_conf") ~ "95% CI") |>
  tab_footnote(md("**Source**: European Social Survey (Round 9)<br>
      **Notes**: The estimates are derived from weighted data (*anweight*). 
      Estimates for interactions between education attainment levels were omitted.
      Models also included country fixed-effects")) |>
  tab_style(style = cell_text(align = "left", indent = px(10)), locations = cells_stub()) 

```


\newpage

<!-- % changing the orientation to portrait again -------------------------- -->

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea




# Mobility estimates by country


```{r}
#| label: tbl-acntry
#| tbl-cap: "Mobility effects by country and outcome variable"

# Running code to generate the raw Table1
source("./code/3_EstimatesByCntry.R")

# Generating formatted table

tab_est_c |>
  left_join(tab_sig_c, by = c("cntry", "Outcome", "Origin", "Destination")) |>
  left_join(tab_clabel, by = "cntry") |>
  mutate(Value = if_else(is.na(Estimate), NA, 
                          paste0(as.character(round(Estimate, 3)),Sig))) |>
  select(country, Outcome, Origin, Destination, Value) |>
  pivot_wider(names_from = Destination, values_from = Value) |>
  pivot_wider(names_from = Outcome, values_from = c(L1, L2, L3), names_glue = "{Outcome}_{.value}") |>
  gt(groupname_col = "country") |>
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Equality", columns = starts_with("Equality")) |>
  tab_spanner(label = "Equity", columns = starts_with("Equity")) |>
  tab_spanner(label = "Need", columns = starts_with("Need")) |>
  tab_spanner(label = "Entitlement", columns = starts_with("Entitlement")) |>
  cols_label(ends_with("_L1") ~ "L1",ends_with("_L2") ~ "L2", ends_with("_L3") ~ "L3") |>
  cols_label(Origin ~ md("Parental <br>educ. level")) |>
  sub_missing(columns = everything(), missing_text = "--") |>
  tab_spanner(label = "Respondents' educational level", columns = -c(Origin, country)) |>
  tab_style_body(fn = function(x) str_detect(x, "\\*"), style = cell_text(weight = 'bold')) |>
  tab_footnote(md("**Source**: European Social Survey (Round 9)<br>
      **Notes**: *p < .05,  **p< .01, ***p < .001. Only countries with a statistically significant effect are shown in the table.")) |>
  tab_style(cell_text(indent = px(-5)), locations = cells_row_groups(groups = everything())) |>
  tab_style(cell_text(indent = px(15)), locations = cells_body(columns = "Origin"))

```



# Missing Values

For the analysis reported in the main text, the missing values were replaced using an iterative multiple imputation method based on the random forest algorithm. Here we include the 


# References